---
title: "NYPD_Coursera_01"
author: "Aaron_H"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplR)
library(tidyverse)
library(ggplot2)

```{r import, echo = TRUE}
NYPD_S <- read.csv("C:/Users/aaron/Documents/NYPD_Shooting_Incident_Data__Historic_ (1).csv")
```

## Tidying

For this coursera submission, I will be going through eact step guided by the course. First I will import the data. Here is the First 10 rows of the imported NYPD report. I tidied the data to the ones I need, which is only the first four columns.




```{r NYPD, echo = TRUE}
NYPD <- head(NYPD_S, 10)
NYPD[,1:4]
```

## Visualization

For this part, I will attempt to group the report based around each date of time of having occured. Then, I will count how many incidents occured on each date. Below is the code.

```{r analysis, echo = TRUE}

NEW_NYPD <- NYPD_S %>%
  arrange(OCCUR_DATE) %>%
  group_by(OCCUR_DATE) %>%
  summarize(BORO = n()) %>%
  mutate(number_of_incidents = BORO) %>%
  select(OCCUR_DATE,number_of_incidents)

NEW_NYPD
  

```

For a clearer presenation, I used this new table to create a bar graph below.

## Visulization 2

Here I will attempt to find the ratio of Male to Female Suspects.

```{r visu, echo = TRUE}

Male = NYPD_S %>%
  filter(PERP_SEX == 'M') %>%
  nrow()

Female = NYPD_S %>%
  filter(PERP_SEX == 'F') %>%
  nrow()

Ratio = Male/Female

Ratio

```

### Result and Bias
This shows that around for 36 times, Male have committed violence. This is only around, because many informations are 'null', meaning I cannot say either least or most. Regardless, 36 times is hard to beat even if many cells are null.

## Modeling

Now using the new table(NEW_NYPD), I will create a bar graph indicating the trend of incidents through out the decade.

```{r modeling, echo = TRUE}
PLOT_NYPD <- ggplot(NEW_NYPD , aes(x = OCCUR_DATE , y = number_of_incidents)) + geom_col()

PLOT_NYPD



```

## Summary

I computed a new table, informing the number of incidents on each date. I created a Male to Female ratio on suspects in an attempt to compare who committed crimes more. Then I created a bargraph presenting the number of incidents through the decade in a clear manner. Except the Male to Female ratio calculation, the incidental date should have no bias alone because incidents were recorded only when it happened.
